---
title: "Interactions"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

<center>The Environmental Interactions tool provides an overview of the number of available Tethys references on Stressor-Receptor interactions.</center>
<br>
<br>
<center>To navigate the matrix, choose a Receptor (rows) and Stressor (column) of interest, and select the hyperlinked (blue) number at the intersection of that column and row. This number indicates the total number of Tethys reference documents available for that Stressor-Receptor interaction and is linked to the "Knowledge Base" page on Tethys website, which provides the available literature.</center>

```{r}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(dplyr, DT, glue, here, kableExtra, knitr, readr, tidyr)

s_r_csv <- ifelse(
  Sys.info()['sysname'] == "Linux",
  "/share/github/mhk-env_shiny-apps/data/tethys_intxns.csv",
  here("data/tethys_stressor_receptor.csv")) # OLD; now updated on server within shiny repo

s_r <- read_csv(s_r_csv)

s_r %>% 
  mutate(
    link     = 
      if_else(
        num_refs > 0,
        glue("<a href='{url}' target='_blank'>{if_else(num_refs == 50, '50+', as.character(num_refs))}</a>"),
        "0")) %>% 
  select(stressor, receptor, link) %>% 
  pivot_wider(names_from = "stressor", values_from = link) %>% 
  # datatable(
  #   escape    = F,
  #   rownames  = T,
  #   options   = list(
  #       pageLength = Inf, 
  #       #dom        = 't',
  #       searching  = F, 
  #       bPaginate  = F, 
  #       info       = F)) %>% 
  kable("html", escape = F) %>%
  kable_styling(
    "striped", full_width = F)
```

