---
title: "Projects"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(here)
library(glue)
library(readr)
library(dplyr)
library(purrr)
library(stringr)
library(sf)
library(leaflet)
# library(DT)
library(markdown)
library(htmltools)
```

This page provides an overview of all past and present Marine Energy projects in the United States at different levels of development and provides active links to permitting documents from either the <a href="https://elibrary.ferc.gov/eLibrary/search" target="_blank">FERC eLibrary</a> or <a href="https://tethys.pnnl.gov/knowledge-base" target="_blank">Tethys Knowledge Base</a>.
<br>
<br>

## Map

To learn more about a project, select the blue pin on the map with your cursor and a pop up will open with the project's name, timeline, geographic coordinates and a list of all submitted permitting and licensing materials to date. Where available, the permitting/licensing documents have been linked to a downloadable PDF of the document or to pages with additional information.
<br>
<br>
```{r map}
sites_csv <- "/share/github/mhk-env_shiny-apps/data/project_sites.csv"

sites <- read_csv(sites_csv) 

# sites %>% 
#   filter(project_name == "WETS") %>% 
#   pull(popup_html)
# 
sites$label_html <- sites$label_html %>% lapply(HTML)
sites$popup_html <- sites$popup_html %>% lapply(HTML)

leaflet(
  data = sites, width = "100%") %>% 
  addProviderTiles(providers$Esri.OceanBasemap) %>% 
  addMarkers(
    label        = ~label_html, 
    popup        = ~popup_html)
```


## Timeline

The figure below shows all past and present Marine Energy projects and the permitting milestones of each over time organized by energy type (riverine, tidal, and wave). You can access relevant FERC documents per project and permitting milestones by clicking on the triangles in the plot. 
<br>

```{r}
library(dplyr)
library(htmltools)
library(htmlwidgets)
library(jsonlite)
library(plotly)
library(ggplot2)
#library(ggiraph)
library(RColorBrewer)

prj_times_csv   <- "/share/github/mhk-env_shiny-apps/data/project_times.csv"
prj_permits_csv <- "/share/github/mhk-env_shiny-apps/data/project_permits.csv"

d_permits <- read_csv(prj_permits_csv)
d_times   <- read_csv(prj_times_csv)

#Create factored list for permit type and technology type for plotting symbols/colors
d_permits$permit_type <- factor(d_permits$permit_type, 
                        levels = c("Notice of Intent/Preliminary Permit Application",
                                   "Draft Pilot License App",
                                   "Final Pilot License App",
                                   "Pilot License Issued",
                                   "Draft License App",
                                   "Draft Re-License App",
                                   "Final License App",
                                   "Final Re-License App",
                                   "Environmental Assessment",
                                   "Settlement Agreement",
                                   "Permit Issued",
                                   "Re-License Issued"))

d_permits$technology_type <- factor(d_permits$technology_type, 
                            levels = c('Riverine Energy', 
                                       'Tidal Energy', 
                                       'Wave Energy'))

d_times$technology_type <- factor(d_times$technology_type, 
                            levels = c('Riverine Energy', 
                                       'Tidal Energy', 
                                       'Wave Energy'))

###ggplot figure that has points and bars indicating permitting
#the fig.width and fig.height above determine the figure size overall

#pick the color and shape scale
scale <- brewer.pal(n=10, name = 'PiYG')
scale <- scale[c(1:5, 5, 7, 7:10, 10)]
shp   <- c(rep(24, 3), 25, 24, 25, 24, 25, rep(24, 3), 25) 

#the input to ggplot is what determines the tooltip label
g <- ggplot(d_permits, 
            aes(text = paste('License Date: ', license_date, '\nProject Name: ', project_name, '\nPermit Type: ', permit_type))) +
  
  #the segment is a gray bar that covers the time period of the permits
  geom_segment(data = d_times, 
               aes(x = date_beg, y = project_name, xend = date_end, yend = project_name, color = project_status), size = 4) +
  
  #the points have colors and shapes indicating different permit types
  geom_point(data = d_permits, 
             aes(x = license_date, y = project_name, fill = permit_type, shape = permit_type), size = 4, stroke = 0) +
  scale_color_manual(name = "", values = c("#30A4E1", "#999999"), breaks = c("Active Project", "Inactive Project"))+
  scale_fill_manual(name = "", values = scale) + 
  scale_shape_manual(name = "", values = shp) +
  
  #label the plot
  labs(title = "MHK Project Timeline", x = "Year of Project", y = "") +
  
  facet_grid(rows = vars(technology_type), scales='free_y', space = 'free') +
  
  #choose a theme
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        #legend.margin=margin(100,100,100,100),
        #legend.box.margin=margin(20,20,20,20),
        #legend.position = c(0.9, 0.84),
        #legend.background = element_rect(fill = "transparent", colour = NA),
        #axis.text.y = axis.groups(unique(d_times$technology_type)),
        axis.text.x = element_text(color="black", size=12, angle=45, vjust=1, hjust = 1),
        axis.text.y = element_text(color="black", size=12, vjust = -1),
        axis.title.y=element_text(face="bold", size=13),
        axis.title.x=element_text(face="bold", size=13),
        plot.margin = margin(.15, .2, 0, 2.5, "cm"),
        plot.background = element_rect(fill = "transparent", colour = NA))

# interactive plot with tooltip
#specify the tooltip in the ggplotly function to get custom text
p = ggplotly(g, tooltip = 'text', height = 700, width = NULL)
#p

##this part is from stackoverflow and works to adjust the y axis ticks and labels, as well as partly adjust the gray bars on the right
len <- length(unique(d_times$technology_type))

total <- 1
for (i in 1:len) {
  total <- total + length(p[['x']][['layout']][[paste('yaxis', i, sep='')]][['ticktext']])
}

spacer <- 0.01 #space between the horizontal plots
total_length = total + len * spacer
end <- 1
start <- 1

# fix y-axis tick marks: yaxis, yaxis2, yaxis3
#for (i in c('', seq(1, len))) { # i = 1
for (i in seq(1, len)) { # i = 1
  yaxis <- ifelse(
    i == 1,
    "yaxis",
    paste0('yaxis', i))
  
  tick_l <- length(p[['x']][['layout']][[yaxis]][['ticktext']]) + 1

  #fix the y-axis
  p[['x']][['layout']][[yaxis]][['tickvals']] <- seq(1, tick_l)
  p[['x']][['layout']][[yaxis]][['ticktext']][[tick_l]] <- ''

  end <- start - spacer
  start <- start - (tick_l - 1) / total_length
  v <- c(start, end)
  #fix the size
  p[['x']][['layout']][[yaxis]]$domain <- v
}

#fix the first entry which has a different name than the rest
p[['x']][['layout']][['annotations']][[3]][['y']] <- (p[['x']][['layout']][['yaxis']]$domain[2] + p[['x']][['layout']][['yaxis']]$domain[1]) /2
p[['x']][['layout']][['shapes']][[2]][['y0']] <- p[['x']][['layout']][['yaxis']]$domain[1]
p[['x']][['layout']][['shapes']][[2]][['y1']] <- p[['x']][['layout']][['yaxis']]$domain[2]

#fix the rectangle shapes in the background
for (i in seq(0,(len - 2) * 2, 2)) {
  p[['x']][['layout']][['shapes']][[i+4]][['y0']] <- p[['x']][['layout']][[paste('yaxis', i /2 + 2, sep='')]]$domain[1]
  p[['x']][['layout']][['shapes']][[i+4]][['y1']] <- p[['x']][['layout']][[paste('yaxis', i /2 + 2, sep='')]]$domain[2]
}

##this part I added and manually moves all the rest of the labels, the legend, bars, xaxis label, legend title
#change the legend location
p[['x']][['layout']][['legend']]$y <- 0.8
p[['x']][['layout']][['legend']]$x <- 1.1

#change the legend title location
p[['x']][['layout']][['annotations']][[5]]$x <- 1.1
p[['x']][['layout']][['annotations']][[5]]$y <- 0.82

#change the legend title
#p[['x']][['layout']][['annotations']][[5]]$text <- 'Permit Type'

#change the color of a shape to determine which one it is
p[['x']][['layout']][['shapes']][[4]]$fillcolor <- 'rgba(217, 217, 217, 1)'
p[['x']][['layout']][['shapes']][[6]]$fillcolor <- 'rgba(217, 217, 217, 1)'

#3 is top (riverine), 4 is middle (tidal), 5 is legend, 1 is x axis label, 2 is vertical label name, 6 is bottom (wave)
#those designations are for the boxes, the actual labels are screwed up and not attached to the right thing necessarily?
p[['x']][['layout']][['annotations']][[3]]$text <- 'Riverine'
p[['x']][['layout']][['annotations']][[4]]$text <- 'Wave'
p[['x']][['layout']][['annotations']][[2]]$text <- 'Tidal'

#moving vertical y labels to center them
p[['x']][['layout']][['annotations']][[3]]$y <- .94
p[['x']][['layout']][['annotations']][[4]]$y <- .28
p[['x']][['layout']][['annotations']][[2]]$y <- .72

#move the y axis label down
p[['x']][['layout']][['annotations']][[1]]$y <- -.1

#change the size of the bottom gray bar
p[['x']][['layout']][['shapes']][[6]]$y0 <- 0.01

#Modify legend categories to the unique set
leg.sorted <- c("Active Project", 
                "Inactive Project",
                "Notice of Intent/Preliminary Permit Application",
                "Draft Pilot License App",
                "Final Pilot License App",
                "Pilot License Issued",
                "Draft License App",
                "Draft Re-License App",
                "Final License App",
                "Final Re-License App",
                "Environmental Assessment",
                "Settlement Agreement",
                "Permit Issued",
                "Re-License Issued")

leg.1 <- c("Active Project", 
           "Inactive Project")

leg.1.name <- "Project Status"

leg.2 <- c("Notice of Intent/Preliminary Permit Application",
           "Draft Pilot License App",
           "Final Pilot License App",
           "Pilot License Issued",
           "Draft License App",
           "Draft Re-License App",
           "Final License App",
           "Final Re-License App",
           "Environmental Assessment",
           "Settlement Agreement",
           "Permit Issued",
           "Re-License Issued")

leg.2.name <- "Permit Type"

for (i in 1:length(p$x$data)) { 
  n1 <- p$x$data[[i]]$name # and this is how the value is stored in plotly
  n2 <- " "
  for (j in 1:length(leg.sorted)) {
    if (grepl(x = n1, pattern = leg.sorted[j])) {n2 = leg.sorted[j]} # if the plotly legend name contains the original value, replace it with the original value
  }
  p$x$data[[i]]$name <- n2 # now is the time for actual replacement
  
  if (grepl(x = n1, pattern = "1|Re-License|Pilot License Issued")) {
    p$x$data[[i]]$showlegend = TRUE
  }else{
    p$x$data[[i]]$showlegend = FALSE
  }

  p$x$data[[i]]$legendgroup <- n2 # Replace legend group name  
  
}

###Note: cannot add annotations here - probably have to add them at the ggplot level and then can edit them here as needed

d_projects <- d_permits %>%
  arrange(technology_type, permit_type, project_name) %>% 
  nest_by(technology_type, permit_type) %>% 
  nest_by(technology_type)

js <- HTML(paste(
  "
  d_projects = ", toJSON(d_projects, pretty=T), ";
  
  // technology_type facets
  yidx = {'y': 0, 'y2': 1, 'y3': 2};
  
  var myPlot = document.getElementById('PlotlyGraph');
  
  myPlot.on('plotly_click', function(data){
  
    // technology_type
    var yaxis = data.points[0].fullData.yaxis;
    // permit_type
    var legendgroup = data.points[0].data.legendgroup;
    // project
    var pointIndex = data.points[0].pointIndex;
  
    console.log(`yaxis: ${yaxis}`);
    console.log(`legendgroup: ${legendgroup}`);
    console.log(`pointIndex: ${pointIndex}`);
  
    if(typeof legendgroup !== 'undefined' | typeof pointIndex !== 'undefined'){
    
      d_tech     = d_projects[yidx[yaxis]].data; 
      idx_permit = d_tech.findIndex(x => x.permit_type === legendgroup);
      d_permits  = d_tech[idx_permit].data;
      d_project = d_permits[pointIndex];
      link = d_permits[pointIndex].link;
      
      console.log(`project_name: ${d_project.project_name}`);
      console.log(`link: ${link}`);
      if (typeof link !== 'undefined'){
        window.open(link,'_blank');
      }
    }
  });", sep=''))

#tag the plot
p$elementId <- "PlotlyGraph"

#once the plot is rendered, use the js code to make it clickable
tagList(
  p,
  onStaticRenderComplete(js))
```

