---
pagetitle: "Regulations"
output:
  html_document:
    css: [libs/styles.css, libs/regs-state.css]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

# Display state links based on: 
# * [regs-state - Google Sheets](https://docs.google.com/spreadsheets/d/1LOrmOM8fLssEGnuC5KuoYhMYl0NZjtdMO1bJUMZ6doc/edit#gid=0)
```

<h1>
  <a href="./regs.html" style="text-decoration:none;">
  <i class="fa fa-arrow-circle-left" style="color:#0b56a6"></i>
  </a>&nbsp;Regulations
</h1>

<br>

## State-led Processes

While there are some similarities in state-specific processes that derive from federal mandates and regulations, each state differs with regard to its regulatory process for MHK projects.  Typically, state regulatory activities take place in the context of the federal processes, e.g., U.S. Army Corps of Engineers process. 
<br>
<br>
The <a href="https://openei.org/wiki/RAPID/Hydropower" target="_blank">Hydropower Toolkit</a> within the Regulatory and Permitting Information Desktop (RAPID) Toolkit of OpenEI provides regulatory information for riverine projects in specific states where it is available.
<br>
<br>

  <div class="diagram-container">
  <!-- state selection -->
  <div id="state-decision">
  <select class="custom-select" id="stateSelect">
  <option value="select-none" selected>Select State:</option>
  
```{r, results='asis'}
library(librarian)
shelf(dplyr, glue, purrr, readr, stringr, tidyr)

g_key   <- "1LOrmOM8fLssEGnuC5KuoYhMYl0NZjtdMO1bJUMZ6doc"
g_sheet <- "1"
g_url <- glue("https://docs.google.com/spreadsheets/d/{g_key}/gviz/tq?tqx=out:csv&sheet={g_sheet}")

d <- read_csv(g_url) %>% 
  nest_by(state) %>% 
  mutate(
    state_code = map_chr(
      state,
      function(s){
        # s = "Rhode Island"
        str_to_lower(s) %>% 
          str_replace_all(" ", "-") }),
    state_html = glue('<option value="{state_code}">{state}</option>'))

d %>% 
  pull(state_html) %>% 
  paste(collapse = "\n") %>% 
  cat()
```

  </select>
  </div>

  <!-- dynamic state selection -->
  <div id="state-selection">
  <div style="height:20px;"></div>
  <div class="state-content" id="select-none"></div>

```{r, results='asis'}
d2 <- d %>% 
  unnest(data) %>% 
  mutate(
    item = ifelse(
      is.na(section_link),
      glue("Hello {state}"),
      glue('<a href="{section_link}" target = "_blank">{section_name}</a><br>'))) %>% 
  group_by(state, state_code) %>% 
  summarize(
    items_html = paste(item, collapse = "\n")) %>% 
  mutate(
    state_html = glue(
      '<div class="state-content" id="{state_code}">
       {items_html}
       </div>'))

d2$state_html %>% 
  paste(collapse = "\n") %>% 
  cat()
```

  </div>
</div>


<script>

// add bootstrap table styles to pandoc tables
function bootstrapStylePandocTables() {
  $('tr.header').parent('thead').parent('table').addClass('table table-condensed');
}
$(document).ready(function () {
  bootstrapStylePandocTables();
});


</script>


<!-- get user option select -->
<script>
select = document.getElementById("stateSelect");
select.onchange = function() {
  var selected = document.getElementById("stateSelect");
  var index = selected.selectedIndex;
  var state = document.getElementsByTagName("option")[index].value;

  var x = document.getElementsByClassName("state-content");
  var i;
  for (i=0; i<x.length; i++) {
      x[i].style.display = "none";
  }

  var y = document.getElementById(state).id;
  var z = document.getElementById(y);
  z.style.display = "block";
}
</script>

